Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-08-14 Scripts/Initial_Analysis.Rmd
small updates

  Spp_Dist <- read_dbem_ens(
    taxon_key = taxon_key,
    year = year,
    data_type = data_type,
    ensemble = ensemble,
    path = my_path("G","DBEM")
  )

@@

@@

    }
    # Determine the ids
    Ids <- unique(Neighbours_combo$neighbour_id)

@@

# head(Test_centroids)
# unique(Test_centroids$ensemble)
# unique(Test_centroids$neigh)
# 
# ggplot(Test_centroids) +
#   geom_line(
#     aes(
#       x = year,
#       y = distance,
#       color = eez_name
#     )
#   )

@@

  # Transboundary Index
  Trans_index <- Centroids_id %>% 
    left_join(historical,
              by = c("taxon_key","eez_name","ensemble","neighbour_id")
    ) %>%
    # Re arrenging table for mutate
    gather("variable","value",distance:hd_temp_sd) %>%
    ungroup() %>% 
    mutate(value = ifelse(is.na(value),0,value)) %>% 
    mutate(
      names = ifelse(eez_name ==Unique_EEZs[1],paste("Country_A",variable,sep="_"),paste("Country_B",variable,sep="_")
    )
    ) %>%
    select(-eez_name,-variable) %>%
    spread(names,value) %>% 
    # mutate index
    mutate(
      trans_index = (Country_A_distance/Country_A_hd_temp_sd - Country_B_distance/Country_B_hd_temp_sd)^2
    # )
    ) %>% 
    # Ten years average of results
    group_by(taxon_key,ensemble,neighbour_id) %>% 
    mutate(RMean = rollmean(x = trans_index, 
                            10, 
                            align = "right", 
                            fill = trans_index)
    ) %>% 
    # filter(year > 1960) %>%
    select(taxon_key,neighbour_id,year,ensemble,trans_index,RMean)

  # Average of 10 years mean of ensemble members results
  mean_sd_index <- Trans_index %>% 
    group_by(taxon_key,year,neighbour_id) %>% 
    summarise_at(vars("RMean"),
                 c(trend=mean,
                   ensemble_sd=sd,
                   n_ens = ~n()
    )
    )

@@

  # Estimate noice from ensemble members
  historic_sd <- Trans_index %>% 
    filter(year <= Hist_y) %>% 
    group_by(taxon_key,neighbour_id,ensemble) %>% #Average historic data per ensemble
    summarise_at(vars("trans_index"),
                 c(trend= mean)
                 ) %>% 
    group_by(taxon_key,neighbour_id) %>% #Capture ensemble variation
    summarise_at(vars("trend"),
                 c(hist_mean=mean,
                   noise=sd,
                   n_ens = ~n())
                 )

@@

  ggplot() +
    geom_line(data = mean_sd_index,
              aes(
                x = year,
                y = trend
              )
    ) +
    geom_ribbon(data = mean_sd_index,
                aes(x=year,
                    ymin=historic_sd$hist_mean-historic_sd$noise,
                    ymax=historic_sd$hist_mean+historic_sd$noise),
                alpha = 0.5,
                fill = "grey50"
    ) +
    geom_ribbon(data = mean_sd_index,
                aes(x=year,
                    ymin=historic_sd$hist_mean-(historic_sd$noise*2),
                    ymax=historic_sd$hist_mean+(historic_sd$noise)*2)
                ,
                alpha = 0.5,
                fill = "grey30"
    ) +
    geom_line(data = mean_sd_index,
              aes(
                x = year,
                y = historic_sd$hist_mean
              ),
              colour = "grey50"
    ) +
    # Conditional, will only plot circles if the data exists
    {if(Plot_Test)geom_point(data = subset(mean_sd_index, trend > (historic_sd$hist_mean+historic_sd$noise) | trend < (historic_sd$hist_mean-historic_sd$noise)),
               aes(
                 x = year,
                 y = trend,
                 colour = "red",
               ),
               shape = 1,
               size = 3
    )
      } +
    geom_vline(xintercept = Hist_y,colour="blue",alpha = 0.5) +
    scale_x_continuous(breaks = seq(1950,2100,5)) +
    theme_classic() +

@@

GetTransIndex <- function(taxon_key,
                          year,
                          Hist_y,
                          data_type = "Catch",
                          path,
                          ensemble_list,
                          Neighbours,
                          eez_centroid,
                          Plot = F){
  t_start <- Sys.time()
  print("Starting Step One")
    # First step
    # Call Get centroids fucntion for centroids data per ensemble
    Step_one <- bind_rows(
      lapply(ensemble_list,
             GetCentroids,
             taxon_key = taxon_key,
             year = year_df$year,
             data_type = data_type,
             Neighbours = Neighbours,
             eez_centroid = eez_centroid
             )
    )

@@

# SAU relations between INDEX and Country's EEZs (see chunk 3)
index_code <- my_path("G", extra_path = "Spatial/SAU/", name="SAU_matching_names.csv", read = TRUE)

>>>>

  Spp_Dist <- read_dbem_ens(
    taxon_key = taxon_key,
    year = year,
    data_type = data_type,
    ensemble = ensemble, # change me to ensemble
    path = my_path("G","DBEM")
  )

@@

       ### Code to produce graphs for Brazil and ruguay

       # name <- paste(taxon_key, "distrbution p = 90%") 
       # Centroids %>% 
       #   # filter(year %in% c(1951,2000,2010)) %>% 
       #   ggplot() +
       #   geom_point(
       #     aes(
       #       x = lon,
       #       y = lat,
       #       size = distance,
       #       color = year,
       #       shape= eez_name
       #     )
       #   ) +
       #   geom_point(
       #     aes(
       #       x = longitude,
       #       y = latitude,
       #     ),
       #     fill = "red"
       #   ) +
       #   geom_sf(data = braur_sf,
       #           aes()
       #   )  +
       #   ggtitle(name)
       # 
       # ggsave(paste(taxon_key,"distribution.jpg",sep="_"),
       # plot = last_plot(),
       # width = 10,
       # height = 8,
       # units = "in",
       # path = my_path("D")
       # )

@@

    # Determine the ids
    Ids <- unique(Neighbours_combo$neighbour_id)

@@

# head(Test_centroids)
# unique(Test_centroids$ensemble)
# unique(Test_centroids$neigh)
#

# braur_sf <- World_ %>% 
#   filter(name %in% c("Brazil","Uruguay"))

# ggplot(braur_sf) +
#   geom_sf() +
  # geom_point(data = subset(Centroids, year %in% seq(1951,2100,20)),
  # geom_point(data = subset(Centroids,eez_name =="Brazil"),
  # geom_point(data = Centroids,
  #            aes(
  #              x = lon,
  #              y = lat,
  #              color = year#,
  #              # size = value
  #            )
  # ) #+
  # facet_wrap(~to_filter+eez_name)

@@

  # Transboundary Index
  Trans_index <- Centroids_id %>% 
    left_join(historical,
              by = c("taxon_key","eez_name","ensemble","neighbour_id")
    ) %>%
    # Re arrenging table for mutate
    gather("variable","value",distance:hd_temp_sd) %>%
    ungroup() %>% 
    mutate(value = ifelse(is.na(value),0,value)) %>% 
    mutate(
      names = ifelse(eez_name ==Unique_EEZs[1],paste("Country_A",variable,sep="_"),paste("Country_B",variable,sep="_")
    )
    ) %>%
    select(-eez_name,-variable) %>%
    spread(names,value) %>% 
    # mutate index
    mutate(
      trans_index = (Country_A_distance/Country_A_hd_temp_sd - Country_B_distance/Country_B_hd_temp_sd)^2
    # )
    ) %>% 
    # Ten years average of results
    group_by(taxon_key,ensemble,neighbour_id) %>% 
    mutate(RMean = rollmean(x = trans_index, 
                            10, 
                            align = "right", 
                            fill = trans_index,
                            na.rm=T)
    ) %>% 
    # filter(year > 1960) %>%
    select(taxon_key,neighbour_id,year,ensemble,trans_index,RMean)

  # Average of 10 years mean of ensemble members results
  mean_sd_index <- Trans_index %>% 
    group_by(taxon_key,year,neighbour_id) %>% 
    summarise_at(vars("RMean"),
                 c(trend=mean,
                   ensemble_sd=sd,
                   n_ens = ~n()

    ),
    na.rm=T
    )

@@

  # Estimate noice from ensemble members
  historic_sd <- Trans_index %>% 
    filter(year <= Hist_y) %>% 
    group_by(taxon_key,neighbour_id,ensemble) %>% #Average historic data per year first
    summarise_at(vars("trans_index"),
                 c(trend= mean),
                 na.rm=T
                 ) %>% 
    group_by(taxon_key,neighbour_id) %>% #Capture ensemble variation
    summarise_at(vars("trend"),
                 c(hist_mean=mean,
                   noise=sd,
                   n_ens = ~n())
                 )

@@

  ggplot() +
    geom_line(data = mean_sd_index,
              aes(
                x = year,
                y = trend
              )
    ) +
    geom_ribbon(data = mean_sd_index,
                aes(x=year,
                    ymin=historic_sd$hist_mean-historic_sd$noise,
                    ymax=historic_sd$hist_mean+historic_sd$noise),
                alpha = 0.5,
                fill = "grey50"
    ) +
    geom_ribbon(data = mean_sd_index,
                aes(x=year,
                    ymin=historic_sd$hist_mean-(historic_sd$noise*2),
                    ymax=historic_sd$hist_mean+(historic_sd$noise)*2)
                ,
                alpha = 0.5,
                fill = "grey30"
    ) +
    geom_line(data = mean_sd_index,
              aes(
                x = year,
                y = historic_sd$hist_mean
              ),
              colour = "grey50"
    ) +
    # Conditional, will only plot circles if the data exists
    {if(Plot_Test)geom_point(data = subset(mean_sd_index, trend > (historic_sd$hist_mean+historic_sd$noise) | trend < (historic_sd$hist_mean-historic_sd$noise)),
               aes(
                 x = year,
                 y = trend,
                 colour = "red",
               ),
               shape = 1,
               size = 3
    )
      } +
    geom_vline(xintercept = Hist_y,colour="blue",alpha = 0.5) +
    scale_x_continuous(breaks = seq(1950,2100,5)) +
    theme_classic()

@@

GetTransIndex <- function(taxon_key,
                          year,
                          Hist_y,
                          data_type = "Catch",
                          path,
                          ensemble_list,
                          Neighbours,
                          eez_centroid,
                          Plot = F){
  t_start <- Sys.time()
  print("Starting Step One")
    # First step
    # Call Get centroids fucntion for centroids data per ensemble

  Step_one <- bind_rows(
      lapply(ensemble_list,
             GetCentroids,
             taxon_key = taxon_key, # for testing
             year = year_df$year,
             data_type = data_type,
             Neighbours = Neighbours,
             eez_centroid = eez_centroid
             )
    )

@@
